---
title: "4rd chapter- parasites"
author: "Melissa Pavez-Fox"
date: "15/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(stringr)
library(tidyr)
library(magrittr)
library(readxl)
library(rstan)
library(dplyr)
library(igraph)
library(brms)
library(beepr)#beeping
library(emmeans)#post-hoc conditional means
library(DHARMa)#model fit
library(bayestestR)#compute 89% CI
library(sjPlot)#extract tables
library(tidybayes)#Plot posteriors
library(reshape2)#Plot

```


Load data
```{r}
#Define user
user = "mp660"#exeter
#user = "mapf1"#st andrews

#Directory for models
directory = paste0("C:/Users/",user,"/OneDrive - University of St Andrews/PhD/Thesis PhD/Thesis_parasites/Data for Markdown/brms models/")

#Directory for edgelists
dir_edges = paste0("C:/Users/",user,"/OneDrive - University of St Andrews/PhD/Thesis PhD/Thesis_parasites/Data for Markdown/")

#Load parasite count
parasites <- read.csv(paste0(dir_edges,"parasites_final_analyses.txt"))

#Load Bison network metrics
networks = readRDS(paste0(dir_edges,"for_bison/Bison_parasites2.RData"))#only individuals with parasite data
all_members = readRDS(paste0(dir_edges,"for_bison/Bison_all.RData"))#all individuals in groups


#Load demographic file
census <- read.csv(paste0(dir_edges,"Census_Sep2020.csv"))


```


```{r}

#Convert variables into right format
parasites %<>% mutate(id = factor(id),
                      sex = factor(sex),
                      post_hurricane = factor(post_hurricane),
                      group_size = as.numeric(group_size),
                      season = factor(season),
                      age = as.numeric(age),
                      outrank_perc = as.numeric(outrank_perc))


#Excludes two males without agonistic data
parasites %<>% filter(!is.na(outrank_perc))

#How many individuals with focal data?
table(parasites$group) #54 + 16 =70, 30 in V

#How many individuals pre and post hurricane
table(parasites$post_hurricane)#54 pre and 46 post

#How many individuals in total?
length(parasites$id)#100

#How many per sex?#66 F, 34 M
table(parasites$sex)

#Age range
min(parasites$age)
max(parasites$age)#4-25
mean(parasites$age)#10.58

#Histograms of counts
hist(parasites$prot_count, breaks = 20)#Protozoa
hist(parasites$nema_count, breaks = 20)#nematodes

#As we are asking about prevalence, which model the presence/absence, for abundance we can only consider individuals that are infected and omit the zeroes. So basically to ask, if an individual is infected, are there some attributes that makes them more susceptible?

#Exclude zeroes from counts
parasites %<>% mutate(proto_count_NZ = ifelse(prot_count == 0, NA, prot_count))

hist(parasites$proto_count_NZ)#potozoas

```

Measures of parasite risk:
- Presence/absence: presence or absence of infection per parasite species (3 binomial dependent variables)
- Intensity: number of parasites per type per infected host (2 count dependent variables: #nematodes or #protozoa excluding zeroes)


Measures of Sociality:
- Social status: agonistic observations from the three groups (males + females).
- Number of weak partners (degree < threshold): grooming and proximity separately.
- Strength to strong partners (strengt >= threshold): grooming and proximity separately

Covariates:
- Age.
- Sex.
- Pre vs post-hurricane.
- Season (only V had samples collected through rainy and dry season. KK and HH samples were collected during rainy season only)

Analysis using BRMS

Descriptive statistics, prevalence overall and pre/post hurricane
```{r}
#FIRST REPORT PREVALENCE FOR EACH SPECIES OVERALL AND PRE AND POST-HURRICANE (prevalence = number of infected individuals over number of analysed hosts n = 100)

#Overall prevalence
length(parasites$id[parasites$bcoli_present == 1])#60/100 unique individuals infected with B.coli
length(parasites$id[parasites$strongiloid_present == 1])#23/100 unique individuals infected with S. fuelleborni
length(parasites$id[parasites$trichuris_present == 1])#24/100 unique individuals infected with T. trichiura

#Prevalence pre and post hurricane
length(parasites$id[parasites$post_hurricane == 0])#54 animals sampled before hurricane and 46 after
#B coli
length(parasites$id[parasites$bcoli_present == 1 & parasites$post_hurricane == 0])#38/54 unique ind pre-hurricane 
length(parasites$id[parasites$bcoli_present == 1 & parasites$post_hurricane == 1])#22/46 unique ind post-hurricane
#Strongyloides
length(parasites$id[parasites$strongiloid_present == 1 & parasites$post_hurricane == 0])#8/54 unique ind pre-hurricane 
length(parasites$id[parasites$strongiloid_present == 1 & parasites$post_hurricane == 1])#15/46 unique ind post-hurricane
#Trichuris
length(parasites$id[parasites$trichuris_present == 1 & parasites$post_hurricane == 0])#8/54 unique ind pre-hurricane
length(parasites$id[parasites$trichuris_present == 1 & parasites$post_hurricane == 1])#16/46 unique ind post-hurricane

#How many individuals did not harbor any parasite?
sum(parasites$richness == 0)#25

```


Question1: Social status and hurricane effect on infection risk
```{r}

#Prevalence of B. coli
prev_coli = brm(data = parasites,
                family = bernoulli,
                bcoli_present ~ scale(age)*post_hurricane + scale(age)*scale(outrank_perc) + sex + season,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 10000)

#Save model
#saveRDS(prev_coli, file = paste0(directory,"prev_coli.rds"))

prev_coli <- readRDS(paste0(directory,"prev_coli.rds"))#load model
pp_check(prev_coli)#looks okay

#Post-hoc test for significance of slopes
#Age*hurricane
emm = emtrends(prev_coli, pairwise ~ post_hurricane, var = "age")
confint(emm, level = .89)
#Before hurricane: median = 0.186, 89%HPD = 0.039, 0.33
#After hurricane: median = -0.155, 89%HPD = -0.32, 0.00076
#Before vs post at mean age = median 0.34, 89%HPD = 0.12 - 0.568

#Age*rank
emm = emtrends(prev_coli,  pairwise ~ outrank_perc, var = "age", at = list(outrank_perc = c(20,80)))
confint(emm, level = .89)

#At average age = 10.6 years
#low-status (20%) median = 0.173, 89% CI = 0.0295, 0.341
#High-status (80%) median = -0.215, 89% CI = -0.416, -0.019
#low vs High median = 0.525, 89% CI = 0.151, 0.91


#Main effect B.coli infection
prev_coli_main = brm(data = parasites,
                family = bernoulli,
                bcoli_present ~ scale(age) + post_hurricane + scale(outrank_perc) + sex + season,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 10000)

#Save model
#saveRDS(prev_coli_main, file = paste0(directory,"prev_coli_main.rds"))
#prev_coli_main <- readRDS(paste0(directory,"prev_coli_main.rds"))#load model
pp_check(prev_coli_main)#looks okay

#B. coli intensity
int_coli = brm(data = parasites,
                family = lognormal(),
                proto_count_NZ ~ scale(age) + scale(outrank_perc) + post_hurricane + sex + season,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 10000)

#Save model
#saveRDS(int_coli, file = paste0(directory,"int_coli.rds"))

int_coli <- readRDS(paste0(directory,"int_coli.rds"))#load model
pp_check(int_coli)#looks okay


#Prevalence of S. fuelleborni
prev_strongi = brm(data = parasites,
                family = bernoulli,
                strongiloid_present ~ scale(age) + post_hurricane + scale(outrank_perc) + sex + season,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 10000)

#Save model
#saveRDS(prev_strongi, file = paste0(directory,"prev_strongi.rds"))
prev_strongi <- readRDS(paste0(directory,"prev_strongi.rds"))#load model
pp_check(prev_strongi)#looks okay



#Prevalence T. trichiura
prev_trichu = brm(data = parasites,
                family = bernoulli,
                trichuris_present ~ scale(age) + post_hurricane + scale(outrank_perc) + sex + season,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 10000)

#Save model
#saveRDS(prev_trichu, file = paste0(directory,"prev_trichu.rds"))
prev_trichu <- readRDS(paste0(directory,"prev_trichu.rds"))#load model
pp_check(prev_trichu)#looks okay

#Get tables with model outputs
#B. coli prevalence (main effect)
tab_model(prev_coli_main,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#B. coli prevalence (interaction)
tab_model(prev_coli,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#B. coli intensity
tab_model(int_coli,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection intensity",
          show.ci = 0.89)

#S. fuelleborni prevalence
tab_model(prev_strongi,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#T. trichiura prevalence
tab_model(prev_trichu,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)


```


Question 2a: Weak proximity/grooming partners and infection risk

```{r}

#Prevalence of B. coli
#Proximity
prev_coliSNA_weakP = brm_multiple(data = networks,
                family = bernoulli,
                balan_present ~ scale(std_weak_prox) + scale(age) + scale(perc_rank) + sex,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 1000)

#Save model
#saveRDS(prev_coliSNA_weakP, file = paste0(directory,"final/prev_coliSNA_weakP.rds"))

prev_coliSNA_weakP <- readRDS(paste0(directory,"final/prev_coliSNA_weakP.rds"))#load model
#pp_check(prev_coliSNA_weakP)#looks okay


#Grooming
prev_coliSNA_weakG = brm_multiple(data = networks,
                family = bernoulli,
                balan_present ~ scale(std_weak_groom) + scale(age) + scale(perc_rank) + sex,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 1000)

#Save model
#saveRDS(prev_coliSNA_weakG, file = paste0(directory,"final/prev_coliSNA_weakG.rds"))
prev_coliSNA_weakG <- readRDS(paste0(directory,"final/prev_coliSNA_weakG.rds"))#load model
#pp_check(prev_coliSNA_weakG)#looks okay



#Prevalence of S. fuelleborni
#Proximity
prev_strongiSNA_weakP = brm_multiple(data = networks,
                family = bernoulli,
                strongi_present ~ scale(std_weak_prox) + scale(age) + scale(perc_rank) + sex,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 1000)

#Save model
#saveRDS(prev_strongiSNA_weakP, file = paste0(directory,"final/prev_strongiSNA_weakP.rds"))
prev_strongiSNA_weakP <- readRDS(paste0(directory,"final/prev_strongiSNA_weakP.rds"))#load model
pp_check(prev_strongiSNA_weakP)#looks okay


#Grooming
prev_strongiSNA_weakG = brm_multiple(data = networks,
                family = bernoulli,
                strongi_present ~ scale(std_weak_groom) + scale(age) + scale(perc_rank) + sex,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 1000)

#Save model
#saveRDS(prev_strongiSNA_weakG, file = paste0(directory,"prev_strongiSNA_weakG2.rds"))
prev_strongiSNA_weakG <- readRDS(paste0(directory,"final/prev_strongiSNA_weakG.rds"))#load model
pp_check(prev_strongiSNA_weakG)#looks okay


#Prevalence T. trichiura
#Proximity
prev_trichuSNA_weakP = brm_multiple(data = networks,
                family = bernoulli,
                trichu_present ~ scale(std_weak_prox) + scale(age) + scale(perc_rank) + sex,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 1000)

#Save model
saveRDS(prev_trichuSNA_weakP, file = paste0(directory,"final/prev_trichuSNA_weakP.rds"))
prev_trichuSNA_weakP <- readRDS(paste0(directory,"final/prev_trichuSNA_weakP.rds"))#load model
pp_check(prev_trichuSNA_weakP)#looks okay


#Grooming
prev_trichuSNA_weakG = brm_multiple(data = networks,
                family = bernoulli,
                trichu_present ~ scale(std_weak_groom) + scale(age) + scale(perc_rank) + sex,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 1000)

#Save model
#saveRDS(prev_trichuSNA_weakG, file = paste0(directory,"prev_trichuSNA_weakG2.rds"))
prev_trichuSNA_weakG <- readRDS(paste0(directory,"final/prev_trichuSNA_weakG.rds"))#load model
pp_check(prev_trichuSNA_weakG)#looks okay


#GENERATE TABLES WITH MODEL OUTPUTS
#B. coli prevalence: weak proximity
tab_model(prev_coliSNA_weakP,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#B. coli prevalence: weak grooming
tab_model(prev_coliSNA_weakG,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#S. fuelleborni prevalence: weak proximity
tab_model(prev_strongiSNA_weakP,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#S. fuelleborni prevalence: weak grooming
tab_model(prev_strongiSNA_weakG,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#T. trichiura prevalence: weak proximity
tab_model(prev_trichuSNA_weakP,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#T. trichiura prevalence: weak grooming
tab_model(prev_trichuSNA_weakG,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",show.ci = 0.89)

```


Question 2B: Strength to strong grooming partners and infection risk

```{r}

#Prevalence of B. coli
prev_coliSNA_str = brm_multiple(data = networks,
                family = bernoulli,
                balan_present ~ scale(std_topstr_groom) + scale(age) + scale(perc_rank) + sex,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 1000)

#Save model
#saveRDS(prev_coliSNA_str, file = paste0(directory,"final/prev_coliSNA_str2.rds"))

prev_coliSNA_str <- readRDS(paste0(directory,"final/prev_coliSNA_str.rds"))#load model
pp_check(prev_coliSNA_str)#looks okay



#Prevalence of S. fuelleborni
prev_strongiSNA_str = brm_multiple(data = networks,
                family = bernoulli,
                strongi_present ~ scale(std_topstr_groom) + scale(age) + scale(perc_rank) + sex,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 1000)

#Save model
#saveRDS(prev_strongiSNA_str, file = paste0(directory,"final/prev_strongiSNA_str.rds"))
prev_strongiSNA_str <- readRDS(paste0(directory,"final/prev_strongiSNA_str.rds"))#load model
pp_check(prev_strongiSNA_str)#looks okay


#Prevalence T. trichiura
prev_trichuSNA_str = brm_multiple(data = networks,
                family = bernoulli,
                trichu_present ~ scale(std_topstr_groom) + scale(age) + scale(perc_rank) + sex,
                cores = 4,
                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                iter = 1000)

#Save model
#saveRDS(prev_trichuSNA_str, file = paste0(directory,"final/prev_trichuSNA_str.rds"))
prev_trichuSNA_str <- readRDS(paste0(directory,"final/prev_trichuSNA_str.rds"))#load model
pp_check(prev_trichuSNA_str)#looks okay

#GENERATE TABLES WITH MODEL OUTPUTS
#B coli prevalence
tab_model(prev_coliSNA_str,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#S. fuelleborni prevalence
tab_model(prev_strongiSNA_str,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

#T. trichiura prevalence
tab_model(prev_trichuSNA_str,transform =  NULL, show.r2 = F, show.p = T, show.se = T, show.stat = T, show.icc = F, show.re.var = F, dv.labels = "Infection risk",
          show.ci = 0.89)

```


FIGURES
Figure 1: Parasites found

Figure 2: Effect of hurricane and age on B. coli presence.
```{r}

prev_coli <- readRDS(paste0(directory,"prev_coli.rds"))#Load model

#Extract draws from posterior
post <- prev_coli %>%
  epred_draws(newdata = expand_grid(outrank_perc = seq(0,100, by=10), # could also just include a single level for rank
                                    age = seq(4,25,by=1),
                                    season = c("rainy","dry"),
                                    post_hurricane = c("1","0"),
                                    sex = c("F","M")), #
              ndraws = 100,
              re_formula = NA)#

#Set probabilities on scale of y axis
parasites %<>% mutate(bcoli1 = ifelse(bcoli_present == 1, 1.02, -0.02))


post %>%
  ggplot(aes(x = age, y = .epred)) +
  stat_lineribbon(aes(),alpha=0.2, .width = c(0.5, 0.8), linewidth = 0.7,
                   show.legend = FALSE, colour = "gray30") +
  geom_jitter(data = parasites,
                    aes(y = bcoli1 ),
                     size = 2, alpha = 0.2, height = 0.0007) +
   scale_colour_manual(values = c("gray50","khaki")) +
  scale_fill_manual(values = c("khaki","grey")) +
         scale_x_continuous(breaks = seq(5,25,5)) +
         scale_y_continuous(breaks=seq(0,1,0.25)) +
         theme_bw() +
         labs(x = "Age (years)", y = "B. coli infection risk") +
        theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 18))+
  facet_grid(~post_hurricane)


```


Figure 3: Effect of social status and age on B. coli presence
```{r}

prev_coli <- readRDS(paste0(directory,"prev_coli.rds"))#Load model

#Extract draws from posterior
post <- prev_coli %>%
  epred_draws(newdata = expand_grid(outrank_perc = seq(0,100, by=10), # could also just include a single level for rank
                                    age = seq(4,25,by=1),
                                    season = c("rainy","dry"),
                                    post_hurricane = c("1","0"),
                                    sex = c("F","M")), #
              ndraws = 100,
              re_formula = NA)#

#Make social status categorical
post %<>% mutate(rank = ifelse(outrank_perc > 80, "High", "Medium"),
                 rank = ifelse(outrank_perc < 20, "Low", rank))
#Remoe medium rank
post %<>% filter(!(rank == "Medium"))


#categorise raw data but preserve all data points (above 50% high and below low)
df = parasites %>% mutate(rank = ifelse(outrank_perc > 50, "High", "Low"))

#Set probabilities on scale of y axis
df %<>% mutate(bcoli1 = ifelse(bcoli_present == 1, 1.02, -0.02))


post %>%
  ggplot(aes(x = age, y = .epred)) +
  stat_lineribbon(aes(),alpha=0.25, .width = c(0.5, 0.8), linewidth = 0.7,
                  show.legend = FALSE, colour = "gray30") +
  geom_jitter(data = df,
                    aes(y = bcoli1 ),
                     size = 2, alpha = 0.2, height = 0.0007) +
   scale_colour_manual(values = c("gray50","khaki")) +
  scale_fill_manual(values = c("khaki","grey")) +
         scale_x_continuous(breaks = seq(5,25,5)) +
         scale_y_continuous(breaks=seq(0,1,0.25)) +
         theme_bw() +
         labs(x = "Age (years)", y = "B. coli infection risk") +
        theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 18))+
  facet_grid(~rank)

```



SUPPLEMENTARY SECTION

Supplementary analyses
```{r}
HH = networks
num_draws = 100
  for(i in 1:num_draws){
  HH[[i]] = networks[[i]][networks[[i]]$group == "HH",]
  }
KK = networks
for(i in 1:num_draws){
  KK[[i]] = networks[[i]][networks[[i]]$group == "KK",]
}



coliSNA_weakP_HH = brm_multiple(data = HH,
                                  family = bernoulli,
                                  balan_present ~ scale(std_weak_prox) + scale(age) + scale(perc_rank) + sex,
                                  cores = 4,
                                  prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                                  iter = 1000)

saveRDS(coliSNA_weakP_HH, file = paste0(directory,"final/coliSNA_weakP_HH.rds"))
#coliSNA_weakP_HH <- readRDS(paste0(directory,"final/coliSNA_weakP_HH.rds"))#load model


coliSNA_weakP_KK = brm_multiple(data = KK,
                                family = bernoulli,
                                balan_present ~ scale(std_weak_prox) + scale(age) + scale(perc_rank) + sex,
                                cores = 4,
                                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                                iter = 1000)

saveRDS(coliSNA_weakP_KK, file = paste0(directory,"final/coliSNA_weakP_KK.rds"))
#coliSNA_weakP_KK <- readRDS(paste0(directory,"final/coliSNA_weakP_KK.rds"))#load model

coliSNA_weakG_HH = brm_multiple(data = HH,
                                  family = bernoulli,
                                  balan_present ~ scale(std_weak_groom) + scale(age) + scale(perc_rank) + sex,
                                  cores = 4,
                                  prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                                  iter = 1000)

saveRDS(coliSNA_weakG_HH, file = paste0(directory,"final/coliSNA_weakG_HH.rds"))
#coliSNA_weakG_HH <- readRDS(paste0(directory,"final/coliSNA_weakG_HH.rds"))#load model



coliSNA_weakG_KK = brm_multiple(data = KK,
                                family = bernoulli,
                                balan_present ~ scale(std_weak_groom) + scale(age) + scale(perc_rank) + sex,
                                cores = 4,
                                prior = c(prior(student_t(5, 0, 2.5), class = "b")),
                                iter = 1000)
saveRDS(coliSNA_weakG_KK, file = paste0(directory,"final/coliSNA_weakG_KK.rds"))
#coliSNA_weakG_KK <- readRDS(paste0(directory,"final/coliSNA_weakG_KK.rds"))#load model

```


Supp. Figures

Figure S1: distributions of edge weights and threshold
```{r}

list_edges = c("HH_edgelist","KK_edgelist")
group_years = c("HH2016","KK2018")

for(i in 1:length(list_edges)){
   edges = read.csv(paste0(dir_edges,group_years[i],"/",list_edges[i],".csv"))
   if(group_years[i] == "HH2016"){
   groom_thres = edges %>% mutate(groom_events = as.integer(groom_dur/300),#300 = focal length
                                  samp_effT = samp_effT*3600,#convert to seconds
                                  total_obs_events = floor(samp_effT/300),
                                  weight = groom_events/total_obs_events) %>%
                filter(!(weight == 0)) %>% summarise(threshold = min(weight))
   groom_thres = round(groom_thres$threshold,digits = 5)
   prox_thres =  edges %>% mutate(weight = obs_together/samp_effC) %>% 
                            filter(!(weight == 0)) %>% summarise(threshold = min(weight))
   prox_thres = round(prox_thres$threshold,digits = 5)
   }
   else{
   groom_thres = edges %>%  mutate(weight = groom_together/samp_effC) %>%
                            filter(!(weight == 0)) %>% summarise(threshold = min(weight))
   groom_thres = round(groom_thres$threshold,digits = 5)
   prox_thres =  edges %>% mutate(weight = prox_together/samp_effC) %>% 
                            filter(!(weight == 0)) %>% summarise(threshold = min(weight))
   prox_thres = round(prox_thres$threshold,digits = 5)
   }
  assign(paste0(group_years[i],"groom_thres"), groom_thres) 
  assign(paste0(group_years[i],"prox_thres"), prox_thres) 
}

#PLOT (requires laading bison networks)
#Define network
fit_edge = fit_groomHH
threshold_net = thres_HH_groom
#Extract 50 random draws from bison edge model
draws = 100
weights = data.frame(value = as.numeric())

for(i in 1:draws){
temp = data.frame(value = plogis(fit_edge$edge_samples[i,]))
weights = rbind(weights,temp)
  }

#weights goes up to 60 decimals so need to be rounded
weights$value = round(weights$value,digits = 4)

#Find threshold for strong partners excluding non-interacting dyads
thres_str = round(quantile(weights[weights >= threshold_net], 0.75), digits = 4)

###Plot with ggplot
max_x = max(weights$value)
#Plot
ggplot(weights, aes(x = value)) +
  geom_density(colour = "gray48",fill= "orange2", alpha = .7)+
  xlab("Edge weights") + ylab("Count") + 
  scale_x_continuous(breaks = seq(0,max_x, 0.02)) +
  scale_y_continuous(expand = c(0.01,0)) + 
  geom_vline(xintercept = c(threshold_net,#Thresold dyad exist or not
                            thres_str),#Threshold for strong partners (3rd quantile excluding zero)
             size = c(0.4, 0.4),
             lty = c(2,2), color = c("black","red"))+ 
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  
rm(fit_edge,temp,weights,priors)

```


Figure S2: Distribution of weak proximity partners pre and post hurricane.
```{r}

#Sample 20 random draws
nets = sample(networks,20)

#create a dataframe where to store the data
data = data.frame(prox = "",
                  groom= "",
                  group = "")


#Loop through each sample to get prox weak and hurricane status
for(i in 1:20){
   sample = nets[[i]]
   #create temp
   temp = data.frame(prox = sample$std_weak_prox,
                     groom = sample$std_weak_groom,
                     group = sample$group)
   
   data = rbind(data,temp)
}

data = data[-1,]
data %<>% mutate(post_hurricane = ifelse(group == "HH", "Pre", "Post"),
                 prox = as.numeric(prox),
                 groom = as.numeric(groom))

#Plot densities
#FigS2A: weak prox partners
ggplot(data, aes(x = prox, fill = post_hurricane)) + geom_density(alpha = 0.5) + theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ labs(y = "Density", x= "Number of weak proximity partners (std)", fill = "Hurricane status") 

#FigS2B: weak groom partners
ggplot(data, aes(x = groom, fill = post_hurricane)) + geom_density(alpha = 0.5) + theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ labs(y = "Density", x= "Number of weak grooming partners (std)", fill = "Hurricane status") 

```


Figure S3: correlation between measures of sociality from Bison
```{r}

#Get values from 20 draws from each posterior
net_metrics = data.frame(prox_weak = "",
                         prox_weak2 = "",
                         groom_weak = "",
                         groom_weak2 = "",
                         groom_str = "",
                         groom_str2 = "",
                         prox_deg = "",
                         groom_deg = "",
                         perc_rank = "")

n_draws = 50

for(k in 1:n_draws){
  post_n = networks[[k]]
  temp  = data.frame(prox_weak = rep("", 70),
                     prox_weak2 = rep("", 70),
                     groom_weak = rep("", 70),
                     groom_weak2 = rep("", 70),
                     groom_str = rep("", 70),
                     groom_str2 = rep("", 70),
                     prox_deg = rep("", 70),
                     groom_deg = rep("", 70),
                     perc_rank = rep("", 70))
  
  temp$prox_weak = post_n$std_weak_prox
  temp$prox_weak2 = post_n$std_weak_prox2
  temp$groom_weak = post_n$std_weak_groom
  temp$groom_weak2 = post_n$std_weak_groom2
  temp$groom_str = post_n$std_topstr_groom
  temp$groom_str2 = post_n$std_topstr_groom2
  temp$prox_deg = post_n$std_deg_prox
  temp$groom_deg = post_n$std_deg_groom
  temp$perc_rank = post_n$perc_rank
  
  net_metrics = rbind(net_metrics,temp)
}

net_metrics = net_metrics[-1,]
net_metrics %<>% mutate_if(is.character, as.numeric)


#Plot correlogram
library(corrplot)
cor.mat1 <- net_metrics %>% select(rank = perc_rank, "# weak prox < 4th quartile" = prox_weak, "# weak prox < 90%" = prox_weak2, prox_degree = prox_deg, "# weak groom < 4th quartile" = groom_weak,"# weak groom < 90%" = groom_weak2,
                                   "sum > 3rd quartile groom" = groom_str, "sum > 90% groom" = groom_str2, groom_degree = groom_deg)
M <- cor(cor.mat1, method = "pearson", use = "complete.obs")
corrplot(M, type = "upper", order = "original",tl.col = "black", tl.srt = 45)


```

Figure S4: presence/absence infection vs age
```{r}
#keep relevant variables
df1 = parasites %>% select(B.coli = bcoli_present, T.trichiura = trichuris_present, S.fuelleborni = strongiloid_present, 
                           sex,age,outrank_perc) 
for_plot = melt(df1, id.vars = c("sex","age","outrank_perc"))

ggplot(for_plot, aes(y= value, x= age)) + 
    geom_violin(position= "dodge",trim= FALSE, alpha= 0.5, show.legend=FALSE) +
  geom_boxplot(aes(y= value, x= age), position=position_dodge(width = 0.895), width=0.1, outlier.colour= "gold4", outlier.size = 1.5, show.legend=FALSE)+
  geom_jitter(aes(fill=value), size= 1.5, alpha=0.6,show.legend=FALSE) +
  facet_wrap(~variable) + labs(y = "Presence of infection", x = "Age (years)") 


```

Figure S5: presence/absence infection vs rank
```{r}
#keep relevant variables
df1 = parasites %>% select(B.coli = bcoli_present, T.trichiura = trichuris_present, S.fuelleborni = strongiloid_present, 
                           sex,age,outrank_perc) 
for_plot = melt(df1, id.vars = c("sex","age","outrank_perc"))

ggplot(for_plot, aes(y= value, x= outrank_perc)) + 
    geom_violin(position= "dodge",trim= FALSE, alpha= 0.5, show.legend=FALSE) +
  geom_boxplot(aes(y= value, x= outrank_perc), position=position_dodge(width = 0.895), width=0.1, outlier.colour= "gold4", outlier.size = 1.5, show.legend=FALSE)+
  geom_jitter(aes(fill=value), size= 1.5, alpha=0.6,show.legend=FALSE) +
  facet_wrap(~variable) + labs(y = "Presence of infection", x = "Animals outranked (%)") 


```


Figure S6: presence/absence infection vs sex
```{r}
#Bar plot more useful to plot quantities in both categorical variables
df1 = parasites %>% select(B.coli = bcoli_present, T.trichiura = trichuris_present, S.fuelleborni = strongiloid_present, 
                           sex) 
for_plot = melt(df1, id.vars = c("sex"))
for_plot %<>% group_by(sex,variable,value) %>% summarise(freq = n())


ggplot(for_plot, aes(sex, y = freq, fill = value)) +     
  geom_col(position = 'dodge') + scale_y_continuous(breaks = seq(0,60,10))+
  facet_wrap(~variable) + labs(x = "Sex", fill = "Presence of infection", y = "Count")
                                                        
                                          
```

Figure S7: variation in age pre and post hurricane, and with social status
```{r}
#FigS7A:
#Age and hurricane per group
ggplot(parasites, aes(x = age, fill = post_hurricane)) + geom_density(alpha = 0.45, colour = "black")+ theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + facet_wrap(~group) + labs(x = "Age (years)", y = "Density", fill = "Hurricane status")

#FigS7B:
#Social status and hurricane per group
ggplot(parasites, aes(x = outrank_perc, fill = post_hurricane)) + geom_density(alpha = 0.45, colour = "black")+ theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + facet_wrap(~group)+ labs(x = "Animals outranked (%)", y = "Density", fill = "Hurricane status")

#######

#Age and social status
ggplot(parasites, aes(x = age, y = outrank_perc, colour = post_hurricane)) + geom_point(size = 3)+ theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#Are the interactions for B. coli reflecting the same effect? That is are rank and age collinear?
cor.test(parasites$age,parasites$outrank_perc)#NO

#But what about split by hurricane status
pre = parasites %>% filter(post_hurricane == 0)
cor.test(pre$age,pre$outrank_perc)#NO

post = parasites %>% filter(post_hurricane == 1)
cor.test(post$age,post$outrank_perc)#NO

```

